\begin{center}
    \section*{Preamble }
\end{center}
The Indian Institute of Technology Goa (IIT Goa)\index{IIT Goa} is envisaged as an institute for high quality research and teaching, especially in science and technology. The mission of IIT Goa is "to impart knowledge and provide a unique learning experience to prepare students to be responsible leaders, managers, entrepreneurs, and professionals who will play a leading role in the sustainable development of Goa and the nation as a whole".

IIT Goa offers the undergraduate degree program of Bachelor of Technology (B.Tech.) under various disciplines or academic programs. These academic programs are governed by rules and regulations approved by the senate of IIT Goa which is a statutory and supreme body of the Institute. The rulings of senate chairperson are final with regards to all academic issues. The senate continuously monitors the academic programs and makes appropriate modifications /improvements as and when required. The senate also sets a definite time schedule for various academic activities. 

This manual is intended to set out the procedures and requirements of the undergraduate (UG) degree programs offered at IIT Goa. Such programs fall under the purview of the Senate Under-Graduate Committee (SUGC) who are responsible for drafting the manual. This institute level committee also decides the pace and the continuation of the student in the program on the basis of their overall performance.

IIT Goa is a very student-oriented place and it is the endeavor always to ensure that the students of this Institute get the best of everything that is needed to create outstanding scientists and engineers. Thank you for choosing IIT Goa. I wish all students a very bright future and successful career.